---
title: "matrix and subset"
output: html_notebook
---

1.1
Function sample takes a sample of the specified size from the elements of x . For example
```{r}
x <- seq(from = 1, to = 10, by = 1)
sample(x)

```

```{r}
##[1]  3  4  5  6  7  8  9  2
##[9]  1 10
```

```{r}
# only select five
sample(x, 5)

```
```{r}
##[1]  5  3  4 10  6
```

Using sample , we can select random row from a matrix. For example,
# byrow를 생략하면 default로 FALSE가 설정되어 열방향으로 채워나간다.
```{r}
n <- 3
m <- matrix(1:30, ncol=3)
m
```
```{r}
##     [,1] [,2] [,3]
##[1,]    1   11   21
##[2,]    2   12   22
##[3,]    3   13   23
##[4,]    4   14   24
##[5,]    5   15   25
##[6,]    6   16   26
##[7,]    7   17   27
##[8,]    8   18   28
##[9,]    9   19   29
##[10,]   10   20   30
```

```{r}
m[sample(nrow(m), n), ]
```
```{r}
##     [,1] [,2] [,3]
##[1,]    9   19   29
##[2,]    2   12   22
##[3,]    8   18   28
```
How could you select n random rows from a matrix m where every selected row should be adjacent with
increasing order?
```{r}
k <- 1
m <- matrix(1:30, ncol=3)
a<-sample(nrow(m)-2,k)
m[a:(a+2), ]



m[c(a,a+1,a+2),]
# The result should look like this:
```
```{r}
##     [,1] [,2] [,3]
##[1,]    8   18   28
##[2,]    9   19   29
##[3,]   10   20   30
```

1.2
How could you select n random rows from a matrix m where every selected row should be adjacent with
random order?
#인접한 행렬들이 랜덤하게 뽑히는 경우.
```{r}
k <- 1
m <- matrix(1:30, ncol=3)

a<-sample(nrow(m)-2,k)
b<-m[a:(a+2), ]
b[sample(nrow(b),3),]

# The result should look like this:
```
```{r}
##     [,1] [,2] [,3]
##[1,]    2   12   22
##[2,]    1   11   21
##[3,]    3   13   23
```

2
Let x be a vector such that
```{r}
x <- c(1, 2, 2, 1, 3, 1)
x
```
Here, 1 implies "male" , 2 implies "female" and 3 implies "unknown" .
Therefore x is indeed "male" "female" "female" "male" "unknown" "male" .
```{r}
##[1] 1 2 2 1 3 1
```


Define a character vector lk such that

```{r}
ifelse(x==1,"male",ifelse(x==2,"female","unknown"))

k=c("male","female","unknown")
k[x]
```

```{r}
##[1] "male"    "female"  "female"  "male"    "unknown" "male" 
```

3
In the following code, NA in x is changed to 0 .
```{r}
x <- c(NA, 1, 2, 3)
x[is.na(x)] <- 0
x
```
```{r}
##[1] 0 1 2 3
```

Using a similar method, change every square number in y to 0 .
```{r}
y<-1:20
y[y%%sqrt(y)==0]<-0
y

x<-1:20
ifelse(x%%sqrt(x)==0, x[x%%sqrt(x)==0]<-0, x)

z<-1:20
z[sqrt(z)%%1==0]<-0
z
```
```{r}
 ##[1]  0  2  3  0  5  6  7  8  0 10 11 12 13 14 15  0 17 18 19 20
```

4
upper.tri() returns a matrix of logicals the same size of a given matrix with entries TRUE in the lower or upper
triangle. You can use an additional argument diag to include diagonal or not. For example,
```{r}
(x <- matrix(1:25, nrow=5, byrow=T))
```
```{r}
##     [,1] [,2] [,3] [,4] [,5]
##[1,]    1    2    3    4    5
##[2,]    6    7    8    9   10
##[3,]   11   12   13   14   15
##[4,]   16   17   18   19   20
##[5,]   21   22   23   24   25
```

```{r}
upper.tri(x)
```
```{r}
##      [,1]  [,2]  [,3]  [,4]  [,5]
##[1,] FALSE  TRUE  TRUE  TRUE  TRUE
##[2,] FALSE FALSE  TRUE  TRUE  TRUE
##[3,] FALSE FALSE FALSE  TRUE  TRUE
##[4,] FALSE FALSE FALSE FALSE  TRUE
##[5,] FALSE FALSE FALSE FALSE FALSE
```

```{r}
upper.tri(x, diag=T)
```
```{r}
##     [,1]  [,2]  [,3]  [,4] [,5]
##[1,]  TRUE  TRUE  TRUE  TRUE TRUE
##[2,] FALSE  TRUE  TRUE  TRUE TRUE
##[3,] FALSE FALSE  TRUE  TRUE TRUE
##[4,] FALSE FALSE FALSE  TRUE TRUE
##[5,] FALSE FALSE FALSE FALSE TRUE
```


```{r}
lower.tri(x)
```
```{r}
##      [,1]  [,2]  [,3]  [,4]  [,5]
##[1,] FALSE FALSE FALSE FALSE FALSE
##[2,]  TRUE FALSE FALSE FALSE FALSE
##[3,]  TRUE  TRUE FALSE FALSE FALSE
##[4,]  TRUE  TRUE  TRUE FALSE FALSE
##[5,]  TRUE  TRUE  TRUE  TRUE FALSE
```
Similarly,
```{r}
lower.tri(x, diag=T)
```
```{r}
##     [,1]  [,2]  [,3]  [,4]  [,5]
##[1,] TRUE FALSE FALSE FALSE FALSE
##[2,] TRUE  TRUE FALSE FALSE FALSE
##[3,] TRUE  TRUE  TRUE FALSE FALSE
##[4,] TRUE  TRUE  TRUE  TRUE FALSE
##[5,] TRUE  TRUE  TRUE  TRUE  TRUE
```

Construct a matrix y such that

```{r}
x[lower.tri(x,diag=T)]<-0
y<-x
y
```
```{r}
##     [,1] [,2] [,3] [,4] [,5]
##[1,]    0    2    3    4    5
##[2,]    0    0    8    9   10
##[3,]    0    0    0   14   15
##[4,]    0    0    0    0   20
##[5,]    0    0    0    0    0
```

