---
title: "conditional probability"
output: html_notebook
---
Let¡¯s simulate a family with two children.
Each child is independently determined as a son or daughter with a half chance.
Each child is born on Monday, Tuesday, Wednesday, Thursday, Friday, Saturday, or Sunday with probability
1/7.
Using sample , we can simulate such family.
```{r}
# randomly simulated first baby
gender1 <- sample(c("Son","Daughter"), 1)
day1 <- sample(c("Mon", "Tue", "Wed", "Thu", "Fri", "Sat", "Sun"), 1)
(first <- c(gender1, day1))
```
```{r}
# randomly simulated second baby
gender2 <- sample(c("Son","Daughter"), 1)
day2 <- sample(c("Mon", "Tue", "Wed", "Thu", "Fri", "Sat", "Sun"), 1)
(second <- c(gender2, day2))
```
1. 
What is the probability that the second child is also a son when the first is a son?
Using a loop, i.e., repeat lots of times the above code, check your answer
```{r}
n<-100000
gender1 <- sample(c("son", "daughter"), n, replace=TRUE)
gender2 <- sample(c("son", "daughter"), n, replace=TRUE)
new_n <- gender2[gender1=="son"]
sum(new_n=="son")/length(new_n)





data_gender<-data.frame(gender1,gender2)
k<-subset(data_gender,gender1=="son")
l<-subset(data_gender,gender1=="son" & gender2=="son")
nrow(l)/nrow(k)
```
2.
One of child is a son. Then what is the conditional probability that the another child is also a son?
Using a loop, i.e., repeat lots of times the above code, check your answer.
```{r}
n<-100000
gender1 <- sample(c("son", "daughter"), n, replace=TRUE)
gender2 <- sample(c("son", "daughter"), n, replace=TRUE)
gender <- data.frame(gender1, gender2)
sons <- subset(gender,(gender1=="son")|(gender2=="son"))

count<-subset(sons,(gender1=="son"& gender2=="son"))
nrow(count)/nrow(sons)




data<-data.frame(gender1,gender2)
k<-subset(data,gender1=="son" |gender2=="son")
l<-subset(data,gender1=="son" & gender2=="son")
nrow(l)/nrow(k)
```
3
One of child is a son and born on Monday. Then what is the conditional probability that the another child is also
a son?
Using a loop, i.e., repeat lots of times the above code, check your answer.
```{r}
n<-100000
gender1 <- sample(c("son", "daughter"), n, replace=TRUE)
day1 <- sample(c("Mon","Tue", "Wed", "Thu", "Fri", "Sat", "Sun"),n,replace =TRUE)
gender2 <- sample(c("son", "daughter"), n, replace=TRUE)
day2 <- sample(c("Mon","Tue", "Wed", "Thu", "Fri", "Sat", "Sun"),n,replace =TRUE)

gender<-data.frame(gender1,day1,gender2,day2)

k<-subset(gender,(gender1=="son" & day1=="Mon") | (gender2=="son" & day2=="Mon"))
L<-subset(gender,(gender1=="son" & day1=="Mon")&(gender2=="son") |
                 (gender2=="son" & day2=="Mon") & (gender1=="son"))

nrow(L)/nrow(k)
```






